---
title: "NNTable"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{NNTable}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Setup training data base
In case you have not already setup a training database please run
```{r, results='hide', message=FALSE}
NNtraining::createTrainingDB()
```


## Load required packages

Load the NNR and NNBiostat packages, which will load a number of packages often used 

```{r setup, results='hide', message=FALSE}
library(NNR)
library(NNBiostat)
```

## Get trial access 

We get access to trial 0001 in our training data by the following:

```{r}
(db <- nnaccess("0001", root = "~/training"))
```

Usually we would not supply the root argument as the default is projstat.

## Load data

### Read adsl 
The available datasets can be read by the following command type
```{r}
adsl <- db$adam("adsl")
```

We can filter the data
```{r}
adsl_f <- adsl %>% filter(FASFL == "Y") 
```

And summarise
```{r}
summary <- adsl_f %>% 
  group_by(AGEGR1, RACE, GEOGR1, TRT30P, SEX) %>% 
  summarise(N = n(), .groups = "drop")
```


We can create a table 

```{r, results='hold', comment=""}
summary %>% 
  NNTable("Age group" = "AGEGR1", Race = "RACE", "GEOGR1", "TRT30P", "SEX", "N") %>% 
  addGroupedColumns("GEOGR1", "Age group") %>% 
  addTransWide(TRT30P = list("SEX" = "N")) %>% 
  addFilling(N = 0) %>% 
  addUnderScore()
```
And alter the appearance

```{r, results='hold', comment=""}
table_out <- summary %>%  
  NNTable("Age group" = "AGEGR1", Race = "RACE", "GEOGR1", "TRT30P", "SEX", "N") %>% 
  addGroupedColumns("GEOGR1", "Race") %>% 
  addTransWide("Age group" = list("SEX" = list(TRT30P = "N"))) %>% 
  addFilling(N = 0) %>% 
  addUnderScore()

table_out
```


Save the output together with xml file
```{r, results='hold', comment=""}
sys_foot <- db$exportOutput(table_out, "NNTable_ex1")

sys_foot
```

